\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-04-25 forwards-and-backwards.tex
signposts

\paragraph{One-step convergence to PDE:}

Theorem \ref{thm:nonlocal_convergence},
combined with Proposition \ref{prop:nonlocal_to_local} or~\ref{nonlocalPME to PME}
implies that we can take the limit $N \to \infty$
followed by the limit $\epsilon \to 0$
to obtain solutions to the PDE \eqref{localPDE}.
However, it is of substantial interest to know whether
we can take those two limits simultaneously.
The general case seems difficult,
but we prove such ``diagonal'' convergence in the following situation.

@@

>>>>

Proofs of the results so far, on nonlocal processes, are found in Section~\ref{sec:proofs}.

\paragraph{One-step convergence to PDE:}
Theorem \ref{thm:nonlocal_convergence},
combined with Proposition \ref{prop:nonlocal_to_local} or~\ref{nonlocalPME to PME}
implies that we can take the limit $N \to \infty$
followed by the limit $\epsilon \to 0$
to obtain solutions to the PDE \eqref{localPDE}.
However, it is of substantial interest to know whether
we can take those two limits simultaneously.
The general case seems difficult,
but we prove such ``diagonal'' convergence in the following situation.
The proof is provided in Section~\ref{subsec:one step convergence proof}.

@@

Proofs of results in this section are found in Section~\ref{sec:lookdown_proofs}.
